Capstone Movielens Report

### 2025-02-15 reports/capstone-movielens-report.Rmd
Penalized estimates computed.

```{r}

@@

>>>>

#### Support function
\
We will use the following function to calculate _RMSE_ in this section:
```{r}
reg_rmse <- function(b){
  test_set |> 
    left_join(data.frame(userId = as.integer(names(a)), a = a), by = "userId") |>
    left_join(data.frame(movieId = as.integer(names(b)), b = b), by = "movieId") |>
    mutate(resid = rating - clamp(mu + a + b)) |> 
    filter(!is.na(resid)) |>
    pull(resid) |> rmse()
}

@@

Let's now figure out the $\lambda$ that minimizes the _RMSE_:
```{r}
# Here we will simply compute the RMSE for different values of `lambda` 
n <- colSums(!is.na(y))

sums <- colSums(y - mu - a, na.rm = TRUE)
lambdas <- seq(0, 10, 0.1)

rmses <- sapply(lambdas, function(lambda){
  b <-  sums / (n + lambda)
  reg_rmse(b)
})

# Here is a plot of the RMSE versus `lambda`:
plot(lambdas, rmses, type = "l")
```
Now we can determine the minimal _RMSE_:
```{r}
print(min(rmses))
```

which is achieved for the following $\lambda$:
```{r}
lambda <- lambdas[which.min(rmses)] 
print(lambda)
```

Using this $\lambda$ we can compute the regularized estimates:
```{r}
b_reg <- sums / (n + lambda)

str(b_reg)
```
Finally, let's verify that the penalized estimates $\hat{b}_i(\lambda)$ we have just computed actually result in the minimal _RMSE_ figured out above: 
```{r}
reg_rmse(b_reg)
```
